---
output: 
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# targets-demo

<!-- badges: start -->
<!-- badges: end -->

This repo has a minimal demo of using the [`targets` R package](https://books.ropensci.org/targets/) for workflow management.  Check out the [manual](https://books.ropensci.org/targets/walkthrough.html#inspect-the-pipeline) fir instructions on how to run the pipeline.

## "Real life" examples:

- https://github.com/BrunaLab/lagged-ipms (uses HPC to run dynamic branches in parallel)
- https://github.com/odaniel1/track-cycling (uses `stantargets`)
- https://github.com/ecohealthalliance/mpx-diagnosis (medium complexity)
- https://github.com/noamross/reprotemplate (nice template for reproducibility that uses `targets`)

#### Workflow Diagram:

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
cat(
  "```mermaid",
  targets::tar_mermaid(targets_only = TRUE, reporter = "silent"),
  "```",
  sep = "\n"
)
#this should display correctly on GitHub, or code can be pasted into https://mermaid.live
```

